 

### 2020-09-09 vertical-thermal-review.Rmd
Update vertical-thermal-review.Rmd

---
title: ''
output: word_document
bibliography: references.bib #This can be generated by exporting BibTex file from Zotero
csl: new-phytologist.csl 
nocite: | 
  @zellweger_seasonal_2019 
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

**Authors (so far, not necessarily in final order):** 
Nidhi Vinod^1^
Martijn Slot^2^
Ian McGregor
Elsa Ordway
Marielle Smith
Tyeen Taylor
Kristina J. Anderson-Teixeira^1,2^*

@@

@@

![(*For latest version of table, see tables.pdf.*)](table2.png)

>>>>

---
title: ''
output: word_document
bibliography: references.bib #This can be generated by exporting BibTex file from Zotero
csl: new-phytologist.csl

---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

**Authors (so far, not necessarily in final order):** 
Nidhi Vinod^1^,
Martijn Slot^2^,
Ian McGregor,
Elsa Ordway,
Marielle Smith,
Tyeen Taylor,
Kristina J. Anderson-Teixeira^1,2^*

@@

```{r eval=FALSE, echo=FALSE}
# refs in this table need to go in the nocite field below
```
---
nocite: | 
  @zellweger_seasonal_2019 
---

@@

![(*For latest version of table, see tables.pdf.*)](table2.png)
```{r eval=FALSE, echo=FALSE}
# refs in this table need to go in the nocite field below
```
---
nocite: | 
  @zellweger_seasonal_2019 
---
